30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
fixed conflicts

	\subsection{Disadvantages}	
		While Tor guarantees anonymity, there are some disadvantages using it. The main disadvantage is that the Tor network is slow. According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.

@@

@@

		\subsection{Bootstrapping}

@@

			<hier moet nog een stukje over i2p komen voor degene die dat paper heeft gelezen>

	\section{Tor vulnerabilities and attacks}
		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?]. In this section we will summarize some of the most well known problems with Tor.

		\subsection{Browser based attacks}
			Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}. By misusing the exit policy of Tor one can reduce the time required to perform the analysis.

			By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user. The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server. Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.

			By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches. A similar system can be set up only using the HTML meta refresh tag. To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666.

@@

	\section{Conclusion}
		The conclusion goes here.

	\appendices
%		\section{Proof of the First Zonklar Equation}
%			Appendix one text goes here.

			% you can choose not to have a title for an appendix
			% if you want by leaving the argument blank
%		\section{}
%			Appendix two text goes here.

		% use section* for acknowledgement
%		\section*{Acknowledgment}
%			The authors would like to thank...

		% Can use something like this to put references on a page
		% by themselves when using endfloat and the captionsoff option.
%		\ifCLASSOPTIONcaptionsoff
%		  \newpage
%		\fi

		% trigger a \newpage just before the given reference
		% number - used to balance the columns on the last page
		% adjust value as needed - may need to be readjusted if
		% the document is modified later
		%\IEEEtriggeratref{8}
		% The "triggered" command can be changed if desired:
		%\IEEEtriggercmd{\enlargethispage{-5in}}

		% references section

		% can use a bibliography generated by BibTeX as a .bbl file
		% BibTeX documentation can be easily obtained at:
		% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
		% The IEEEtran BibTeX style support page is at:
		% http://www.michaelshell.org/tex/ieeetran/bibtex/
		%\bibliographystyle{IEEEtran}
		% argument is your BibTeX string definitions and bibliography database(s)
		%\bibliography{IEEEabrv,../bib/paper}
		%
		% <OR> manually copy in the resultant .bbl file
		% set second argument of \begin to the number of references
		% (used to reserve space for the reference number labels box)
	\bibliography{paper_references}

>>>>

	\subsection{Disadvantages}
	\label{ss:tor_disadvantages}

		While Tor guarantees anonymity, there are some disadvantages using it. The main disadvantage is that the Tor network is slow. According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.

@@

	\section{Tor vulnerabilities and attacks}
Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}. In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.

		\subsection{Browser based attacks}
		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}. By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\

		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user. The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server. Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.\\

		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches. A similar system can be set up only using the HTML meta refresh tag. To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\

		\subsection{Low-Resource Routing attacks}
		Hier wat over routing attacks

		\subsection{Sybil attacks}
		Hier wat over sybil attacks

		\subsection{Replay Attacks}
		Hier wat over replay attacks

@@

			\subsection{Bootstrapping new nodes}
		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with. In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.\\

Moving this system to a non peer-to-peer base is difficult. Dingledine et al. stated that this indeed is still an open problem. With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network. Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.

		\subsection{Incentives in decentralized systems}
		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate. There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor. If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified. In other words the incentive data has to be accurate and reliable. Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\

		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network. The first thing that is described is the so called \emph{Warm-glow Model}. In this model determines the percentage of free-rides based on the probabilistic population distribution. If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.\\

		The second proposal is using monetary schemes. While it is not exemplified a lot, the main idea is to use a virtual currency as incentive. The problems with this approach are the scalability and the hidden costs of this service.\\

		The third proposal is \emph{Reciprocity-Based Schemes}. Using this approach a peer maintains a behavior history of other peers in the network. These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity. The formal are more suitable for longer relationships between peers. The latter is more scalable but they rely on third party and must handle trust issues themselves.

@@

@@

	\section{Conclusion}
		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network. Furthermore we looked at the main disadvantages and problems Tor currently has. We then made a bridge to decentralized systems. We first explained which problems one might face when decentralizing a system such as Tor. The next section shows which systems currently have a decentralized structure and/or mechanism. These systems are then compared to each other with their pros and cons.\\

		From this table we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor. The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of  attacks.\\

While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.

	\appendices

	\bibliography{paper_references}
